Comments on Latent Ranking

### 2021-06-23 output_scripts/revisions_may.Rmd
look at further stability components, set sim fits to small examples

@@

@@

return_df %>% 
  filter(observe.id >= start_winds$observe.id[1]) %>% 
  filter(observe.id <= end_winds$observe.id[1]) %>% 
  ### join with wind1_memb, tally
  left_join(wind1_memb, by = c("initiator" = "id"))

# length(lec2$membership)
# 
# length(lec3$membership)

@@

@@

m1_ks <- tibble(Method = "C-HP",
       ks = as.vector(KS_model1_array))

m2_ks <- tibble(Method = "C-DCHP",
       ks = as.vector(KS_model2_array))

m3_ks <- tibble(Method = "C-MMHP",
       ks = as.vector(KS_model3_array))

true_ks <- tibble(Method = "True",
       ks = as.vector(KS_true_array))

@@

m1_pr <- tibble(Method = "C-HP",
       pr = as.vector(PR_model1_array))

m2_pr <- tibble(Method = "C-DCHP",
       pr = as.vector(PR_model2_array))

m3_pr <- tibble(Method = "C-MMHP",
       pr = as.vector(PR_model3_array))

true_pr <- tibble(Method = "True",
                  pr = as.vector(PR_true_array))

>>>>

  init_ranking <- all_ranks %>% filter(when == "first14") %>% 
  group_by(node) %>% 
  summarise(med = median(rank)) %>% 
  arrange(-med) %>% 
  pull(node)

  ### then set the levels off this
  all_ranks$node <- factor(all_ranks$node, 
                           levels = as.character(init_ranking))

@@

### Further Stability Questions

To further investigate the stability of these rankings we 
can do multiple things, including comparing the I&SI scores for both time
periods to see the correlation across time.

```{r compute start-end-isi}
isi_data <- tibble()

for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort, 
                                    full_data[[cohort_names[current_cohort]]],
                                      clean_data)
  start_events <- return_df %>% filter(day <= 14)
  wl_start <- get_wl_matrix(start_events[, c(3, 4)])
  isi_start <- isi98(wl_start)
  start_inf <- tibble(score = isi_start$I + isi_start$SI,
                      order = list(isi_start$best_order),
                      cohort = current_cohort,
                      time = "Start")
  isi_data <- isi_data %>% bind_rows(start_inf)
  end_events <- return_df %>% filter(day > 7)
  wl_end <- get_wl_matrix(end_events[, c(3, 4)])
  isi_end <- isi98(wl_end)
  end_inf <- tibble(score = isi_end$I + isi_end$SI,
                      order = list(isi_end$best_order),
                      cohort = current_cohort,
                      time = "End")
  isi_data <- isi_data %>% 
    bind_rows(end_inf)
}

```{r plot_output}
isi_data %>% ggplot(aes(cohort, score, colour = time)) +
  geom_point(alpha = 0.5, show.guide = FALSE) + 
  scale_x_continuous(breaks = 1:10)

### want one row for each cohort
isi_data %>% 
  select(-order) %>% 
  pivot_wider(names_from = time, values_from = score) %>% 
  summarise(correlation = cor(Start, End))

@@

return_df %>% 
  filter(observe.id >= start_winds$observe.id[1]) %>% 
  filter(observe.id <= end_winds$observe.id[1]) %>% 
  ### join with wind1_memb, tally
  left_join(wind1_memb, by = c("initiator" = "id")) %>% 
  left_join(wind1_memb, by = c("recipient" = "id")) %>% 
  rename(send_clust = memb.x, 
         rec_clust = memb.y) %>% 
  group_by(send_clust, rec_clust) %>% 
  summarise(num_events = sum(no.events)) %>% 
  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
  group_by(clust) %>% 
  summarise(events = sum(num_events)) %>% 
  ungroup() %>% 
  mutate(prop = events/sum(events))

wind2_memb <- tibble(id = 1:12, memb = lec2$membership)

return_df %>% 
  filter(observe.id >= start_winds$observe.id[2]) %>% 
  filter(observe.id <= end_winds$observe.id[2]) %>% 
  ### join with wind1_memb, tally
  left_join(wind2_memb, by = c("initiator" = "id")) %>% 
  left_join(wind2_memb, by = c("recipient" = "id")) %>% 
  rename(send_clust = memb.x, 
         rec_clust = memb.y) %>% 
  group_by(send_clust, rec_clust) %>% 
  summarise(num_events = sum(no.events)) %>% 
  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
  group_by(clust) %>% 
  summarise(events = sum(num_events)) %>% 
  ungroup() %>% 
  mutate(prop = events/sum(events))

wind3_memb <- tibble(id = 1:12, memb = lec3$membership)

return_df %>% 
  filter(observe.id >= start_winds$observe.id[3]) %>% 
  filter(observe.id <= end_winds$observe.id[3]) %>% 
  ### join with wind1_memb, tally
  left_join(wind3_memb, by = c("initiator" = "id")) %>% 
  left_join(wind3_memb, by = c("recipient" = "id")) %>% 
  rename(send_clust = memb.x, 
         rec_clust = memb.y) %>% 
  group_by(send_clust, rec_clust) %>% 
  summarise(num_events = sum(no.events)) %>% 
  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
  group_by(clust) %>% 
  summarise(events = sum(num_events)) %>% 
  ungroup() %>% 
  mutate(prop = events/sum(events))

```{r repeat-all-cohorts}

get_inter_ext_events <- function(current_cohort) {
  total_event_array <- total_event_array_lst[[current_cohort]]
  active_event_array <- active_event_array_lst[[current_cohort]]
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort, 
                                    full_data[[cohort_names[current_cohort]]],
                                      clean_data)

  start_win <- floor(max(return_df$observe.id) / 3) * (0:2) + 1
  end_win <- floor(max(return_df$observe.id) / 3) * (1:3)
  matrix1 <- apply(
    total_event_array[, , start_win[1]:end_win[1]] -
      active_event_array[, , start_win[1]:end_win[1]],
    c(1, 2), sum
  )
  matrix2 <- apply(
    total_event_array[, , start_win[2]:end_win[2]] -
      active_event_array[, , start_win[2]:end_win[2]],
    c(1, 2), sum
  )
  matrix3 <- apply(
    total_event_array[, , start_win[3]:end_win[3]] -
      active_event_array[, , start_win[3]:end_win[3]],
    c(1, 2), sum
  )

  g_community1 <- graph_from_adjacency_matrix(matrix1, mode = "undirected")
  lec1 <- cluster_leading_eigen(g_community1)

  wind1_memb <- tibble(id = 1:12, memb = lec1$membership)

  return_df %>% 
    filter(observe.id >= start_winds$observe.id[1]) %>% 
    filter(observe.id <= end_winds$observe.id[1]) %>% 
    ### join with wind1_memb, tally
    left_join(wind1_memb, by = c("initiator" = "id")) %>% 
    left_join(wind1_memb, by = c("recipient" = "id")) %>% 
    rename(send_clust = memb.x, 
           rec_clust = memb.y) %>% 
    group_by(send_clust, rec_clust) %>% 
    summarise(num_events = sum(no.events)) %>% 
    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
    group_by(clust) %>% 
    summarise(events = sum(num_events)) %>% 
    ungroup() %>% 
    mutate(prop = events/sum(events))

  wind2_memb <- tibble(id = 1:12, memb = lec2$membership)

  return_df %>% 
    filter(observe.id >= start_winds$observe.id[2]) %>% 
    filter(observe.id <= end_winds$observe.id[2]) %>% 
    ### join with wind1_memb, tally
    left_join(wind2_memb, by = c("initiator" = "id")) %>% 
    left_join(wind2_memb, by = c("recipient" = "id")) %>% 
    rename(send_clust = memb.x, 
           rec_clust = memb.y) %>% 
    group_by(send_clust, rec_clust) %>% 
    summarise(num_events = sum(no.events)) %>% 
    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
    group_by(clust) %>% 
    summarise(events = sum(num_events)) %>% 
    ungroup() %>% 
    mutate(prop = events/sum(events))

  wind3_memb <- tibble(id = 1:12, memb = lec3$membership)

  return_df %>% 
    filter(observe.id >= start_winds$observe.id[3]) %>% 
    filter(observe.id <= end_winds$observe.id[3]) %>% 
    ### join with wind1_memb, tally
    left_join(wind3_memb, by = c("initiator" = "id")) %>% 
    left_join(wind3_memb, by = c("recipient" = "id")) %>% 
    rename(send_clust = memb.x, 
           rec_clust = memb.y) %>% 
    group_by(send_clust, rec_clust) %>% 
    summarise(num_events = sum(no.events)) %>% 
    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
    group_by(clust) %>% 
    summarise(events = sum(num_events)) %>% 
    ungroup() %>% 
    mutate(prop = events/sum(events))

}

get_inter_ext_events(current_cohort = 2)

@@

  if(ncol(lam0_draws) != sum(clean_sim_data$N_count >2)) {
    stop("Mismatch between params and event pairs")
  }

@@

m1_ks <- tibble(Method = "C-HP",
       ks = as.vector(KS_model1_array[sims, ,]))

m2_ks <- tibble(Method = "C-DCHP",
       ks = as.vector(KS_model2_array[sims, ,]))

m3_ks <- tibble(Method = "C-MMHP",
       ks = as.vector(KS_model3_array[sims, ,]))

true_ks <- tibble(Method = "True",
       ks = as.vector(KS_true_array[sims, ,]))

@@

m1_pr <- tibble(Method = "C-HP",
       pr = as.vector(PR_model1_array[sims, ,]))

m2_pr <- tibble(Method = "C-DCHP",
       pr = as.vector(PR_model2_array[sims, ,]))

m3_pr <- tibble(Method = "C-MMHP",
       pr = as.vector(PR_model3_array[sims, ,]))

true_pr <- tibble(Method = "True",
      pr = as.vector(PR_true_array[sims, ,]))
